---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fin.backend

This is a basic `R` package used in AI forecasts, which is intended to define loading functions, technical indicator calculations and rebalancing data. Its specific objective is also to calculate\
target values.

This R package is intended to be part of a trading signals application.

## Quick Guide

```{r example}
library(fin.backend)
library(future)
library(ggplot2)

plan(multisession)

dt <- data_tools.load_raw_data("CAC_40", "2022-11-11")

dt_plot <- data_tools.flat_raw_data(dt, 7, "2022-11-11", "2022-06-01")

ggplot(dt_plot[date >= "2022-06-01", .(date, close, Target)]) + geom_line(aes(x = as.Date(date), y = close)) + geom_point(aes(x = as.Date(date), y = close, color = factor(round(Target))))

plan(sequential)
```

## Data

-   Historical FCHI : [Yahoo Finance](https://fr.finance.yahoo.com/quote/%5EFCHI/history?p=%5EFCHI)

-   Historical InterBank exchanges rates : [Banque de France](http://webstat.banque-france.fr/fr/downloadFile.do?id=5385564&exportType=csv)

-   Historical currencies rates : [Banque de France](http://webstat.banque-france.fr/fr/downloadFile.do?id=5385698&exportType=csv)

-   Historical VIX : [Yahoo Finance](https://finance.yahoo.com/quote/%5EVIX/history?period1=631238400&period2=1649462400&interval=1d&filter=history&frequency=1d&includeAdjustedClose=true) CBOE Volatility Index (\^VIX)

-   Other historical VIX : [CBOE](https://cdn.cboe.com/api/global/us_indices/daily_prices/VIX_History.csv)

-   Historical VXD : [CBOE](https://cdn.cboe.com/api/global/us_indices/daily_prices/VXD_History.csv) DJIA Volatility

## Restricted User Guide

### Manage MongoDB

#### Clean-up (if needed)

-   DB is located under `~/PROJETS/fin/fin.db`
-   Delete all files in `./fin.db/mongo-db/*`
-   Delete log file `./fin.db/log/mongo.log`

#### Star the DB

-   DB is located under `~/PROJETS/fin/fin.db`
-   Execute `./fin-db/mongo.sh`

### R Project

-   R project is located under `~/PROJETS/fin/fin.backend`

#### Build with RStudio

-   Onglet `Build` / `More` / `Clean and Install`

```bash
    Restarting R session...

    * Project '~/PROJETS/fin/fin.backend' loaded. [renv 0.16.0]
    > library(fin.backend)
    > 
```

-   Put the downloaded CSV data under `./fin.backend/inst/testdata/` directory
-   Execute the import function `init-db.import_data()`
